# Reproducible Research: Peer Assessment 1

---

## Loading and preprocessing the data

Read in the data.
```{r; echo:TRUE}
activity <- read.csv('activity.csv')
```

Convert the date columns.
```{r}
library(lubridate)
activity <- transform(activity, date=ymd(activity$date))
```

The numbering of the intervals is funny. For example, it goes from 55 to 100. 55 represents the interval from 12:55-1:00 am, and 100 represents the interval from 1:00-1:05 am. To make interpreting graphs and results easier, I'll just convert each interval to the actual start time.
```{r}
activity <- transform(activity, 
                      interval=hm(formatC(interval/100, digits=2, format='f')))
```

## What is mean total number of steps taken per day?

First, calculate the mean number of steps for each day:
```{r}
total.steps <- tapply(activity$steps, activity$date, sum, na.rm=TRUE)
```

Let's look at the mean and median for the total steps per day:
```{r}
mean(total.steps)
median(total.steps)
```

And let's take a look at the distribution of total number of steps per day with a histogram:
```{r}
library(ggplot2)
qplot(total.steps, xlab='Total steps', ylab='Frequency')
```


## What is the average daily activity pattern?

First calculate the average for each five minute period.
```{r}

# There is some kind of issue with the intervals not working as factors...
daily <- tapply(activity$steps, activity$interval, mean, na.rm=TRUE)
daily.df <- data.frame(interval)
```

Now let's look at a graph of a "normal" day.
```{r}
ggplot(daily.df, aes(interval, mean.steps)) +
    geom_line() + 
    xlab('Interval') +
    ylab('Mean number of steps')
```


## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
